Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-09-14 04_paper/0913_draft.Rmd
minor edits

Figure \@ref(fig:aid-debt-country) shows the top-20 Chinese aid and debts recipient countries on average between 2002 and 2017. Notably, on average, Iraq received 500 million in aid but borrows 0 dollars of loan from China. In contrast, Russia borrowed almost 8,000 million dollars from China but received no aid at all. There is little overlap between the top recipient countries that receive both aid and debt from China. There are stark variations in terms of the amounts China lends. Russia and Venezuela were the only countries that borrowed more than 5,000 million dollars debt on average, the sum of which accounted for about 30% of the total lending amounts of the top-20 debt recipients. Eight countries are shown on both the left and right frames: Indonesia, Pakistan, Laos, Ethiopia, Cambodia, Sri Lanka, Kenya, and Sudan. Geographically, five are in South or East Asia, whereas three are in Africa.

In terms of the compositions of debt and aid for the top 20 beneficiaries of total amount of both aid and debt, Figure \@ref(fig:compositions) shows that 14 out of 20 countries received over 80% of debt in their portfolio. The top 5 recipients, Russia, Venezuela, Angola, Kazakhstan and Brazil received support from China almost purely in the form of loans. Kazakhstan is the only exception among the five beneficiaries that received slightly 2\% of aid in its portfolio. We can infer that Beijing invests more heavily in its debt, comparing to its aid distribution. In consistent with the trends demonstrated in Figure \@ref(fig:4-types), China takes a targeted approach with debt.

>>>>

Figure \@ref(fig:aid-debt-country) shows the top-20 Chinese aid and debts recipient countries on average between 2002 and 2017. Notably, on average, Iraq received 500 million in aid but borrows 0 dollars in loans from China. In contrast, Russia borrowed almost 8 billion dollars from China but received no aid at all. There is little overlap between the top recipient countries that receive both aid and debt from China. There are stark variations in terms of the amounts China lends. Russia and Venezuela were the only countries that borrowed more than 5 billion dollars in debt on average, the sum of which accounted for about 30% of the total lending amounts of the top-20 debt recipients. Eight countries are shown on both the left and right frames: Indonesia, Pakistan, Laos, Ethiopia, Cambodia, Sri Lanka, Kenya, and Sudan. Geographically, five are in South or East Asia, whereas three are in Africa.

In terms of the composition of debt and aid for the top 20 beneficiaries of total amount of both aid and debt, Figure \@ref(fig:compositions) shows that financing received in 14 out of 20 countries was over 80% debt. The top 5 recipients, Russia, Venezuela, Angola, Kazakhstan and Brazil received support from China almost purely in the form of loans. Kazakhstan is the only exception among the five beneficiaries with aid comprising a measly 2% of its portfolio. Clearly, we can infer that Beijing invests more heavily in its debt relative to aid. Consistent with the trends demonstrated in Figure \@ref(fig:4-types), China takes a targeted approach with debt.
